method

### 2021-08-10 06_Paper/ER-ED/method.Rmd
added headlines
updated files
added text
added references

---
output: 
  pdf_document:
    keep_tex: true
---

# Method

>>>>

---
output: 
  pdf_document:
    keep_tex: true
bibliography: ER_ED.bib
csl: apa7.csl
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(targets)
```

# 2. Method

"We report how we determined our sample size, all data exlusions (if any), all manipulations, and all measures in the study" in compliance with the 21-word-solution of open science [@simmons2012]

## 2.1 Participants

xxx.

## 2.2

xxx.
